### 2022-01-26 input/introduction.tex
add comments on introduction

Instead, a \process creating a replica should notify all and only
\processes that have no closer replica in the system. This would
create interconnected sets of \processes, or \emph{partitions},
gathered around a \emph{source} being their respective replica. A
\process deleting its replica should notify all members of its
partition so they can identify and rally their new closest
partition. A periodic advertisement protocol already provides both
operations for routing purposes~\cite{hemmati2015namebased}. However,
its functioning requires
\begin{inparaenum}[(i)]
\item to generate traffic even when the system is quiescent, and
\item to finely tune physical-time-based intervals that depend on
  network topology parameters such as network diameter.
\end{inparaenum}

%% A ``simple'' way to tackle the aforementioned limitations would be to
%% maintain on each node composing the infrastructure and for each
%% content, an index of all replicas (and their ``distance'').  In such
%% an approach, each time a new replica is created or deleted, a message
%% is broadcasted from the node that performed the operation (\ie the
%% source) to all nodes, increasing the distance information at each hop.
%% %
%% In addition to being complicated for large-scale systems, maintaining
%% a global view on each node is useless as there is no interest to
%% inform a node of the creation/removal of a replica at the opposite of
%% the network (each node trying to get content from the ``closest''
%% one).  In other words, the broadcast should be limited to a partition
%% of the infrastructure, (\ie the subset of nodes that has to update the
%% current location for this particular content). Obviously, these
%% partitions depend and evolve according to concurrent operations made
%% by nodes (replica creation/removal) as well as dynamic changes in the
%% infrastructure (network failures, node apparitions/leaves).

@@

\item [$\bullet$] We provide an implementation entitled \NAME that
  uses aforementioned principles to \underline{a}dapt its partitioning
  to creations and deletions of partitions even in dynamic systems
  where \nodes join, leave, and crash at any time. \NAME's efficiency
  relies on a communication primitive called
  \underline{s}coped-broad\underline{cast} that enables epidemic
  dissemination of messages as long as receiving \processes verify an
  application-dependant predicate.

>>>>

To mitigate the broadcasting overhead, a \process creating a replica should notify all and only
\processes that have no closer replica in the system. This would
create interconnected sets of \processes, or \emph{partitions},
gathered around a \emph{source} being their respective replica. A
\process deleting its replica should notify all members of its
partition so they can identify and rally their new closest
partition.
% TODO: A periodic protocol... why a periodic protocol solves the ''correct cast/scope''? I miss the point here 
\textcolor{red}{
A periodic advertisement protocol already provides both
operations for routing purposes~\cite{hemmati2015namebased}. However,
its functioning requires
\begin{inparaenum}[(i)]
\item to generate traffic even when the system is quiescent, and
\item to finely tune physical-time-based intervals that depend on
  network topology parameters such as network diameter.
\end{inparaenum}
}
%% A ``simple'' way to tackle the aforementioned limitations would be to
%% maintain on each node composing the infrastructure and for each
%% content, an index of all replicas (and their ``distance'').  In such
%% an approach, each time a new replica is created or deleted, a message
%% is broadcasted from the node that performed the operation (\ie the
%% source) to all nodes, increasing the distance information at each hop.
%% %
%% In addition to being complicated for large-scale systems, maintaining
%% a global view on each node is useless as there is no interest to
%% inform a node of the creation/removal of a replica at the opposite of
%% the network (each node trying to get content from the ``closest''
%% one).  In other words, the broadcast should be limited to a partition
%% of the infrastructure, (\ie the subset of nodes that has to update the
%% current location for this particular content). Obviously, these
%% partitions depend and evolve according to concurrent operations made
%% by nodes (replica creation/removal) as well as dynamic changes in the
%% infrastructure (network failures, node apparitions/leaves).

@@

\item [$\bullet$] We provide an implementation entitled \NAME that
  uses aforementioned principles to \underline{a}dapt its partitioning
  to creations and deletions of partitions even in dynamic systems
  where \nodes join, leave, and crash at any time. \NAME's efficiency
  relies on a communication primitive called
  \underline{s}coped-broad\underline{cast} that enables epidemic
  dissemination of messages as long as receiving \processes verify an
  application-dependant predicate.
  \textcolor{red}{AS-Cast stands for Autonomous System-Cast since xAS means cross AS? what did I miss?}
